Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-07-14 reports/manuscript.Rmd
Final rerun of pipeline
Add effects/studies that met criteria to abstract

abstract: |
  The influence of electronic screens on children and adolescents’ health and education is not well understood.
  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants) on screen time and any outcome for youths.
  Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, `r targets::tar_read(manuscript_info)$abstract$social_media`) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, `r targets::tar_read(manuscript_info)$abstract$edu`).
  Some types of screen use have complex associations with outcomes.
  For example, television viewing showed harmful correlations with learning `r targets::tar_read(manuscript_info)$abstract$tv_edu`.
  However, when parents watched with their children, general screen use was associated with greater literacy `r targets::tar_read(manuscript_info)$abstract$coview`.
  These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 1 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Supplementary File 2.
After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.
These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies, involving `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
The characteristics of the included effects are available in Supplementary File 3.

@@

@@

@@

There were a number of strengths and limitations to our work.
Our primary goal for this umbrella review was to provide a high-level synthesis of screen use research, by examining a range of exposures and the associations with a broad scope of outcomes.
Our results represent the findings from `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.

>>>>

abstract: |
  The influence of electronic screens on children and adolescents’ health and education is not well understood.
  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r targets::tar_read(manuscript_info)$effects_sum$sum_k` primary studies; `r targets::tar_read(manuscript_info)$effects_sum$sum_n` participants) on screen time and any outcome for youths.
  Of these, `r targets::tar_read(manuscript_info)$effects_certain` effects from `r targets::tar_read(manuscript_info)$reviews_certain` met our criteria for statistical certainty.
  Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, `r targets::tar_read(manuscript_info)$abstract$social_media`) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, `r targets::tar_read(manuscript_info)$abstract$edu`).
  Some types of screen use have complex associations with outcomes.
  For example, television viewing showed harmful correlations with learning `r targets::tar_read(manuscript_info)$abstract$tv_edu`.
  However, when parents watched with their children, general screen use was associated with greater literacy `r targets::tar_read(manuscript_info)$abstract$coview`.
  These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.

@@

The most frequently reported exposures were `r manuscript_info$freq_exposures`.
Supplementary File 1 provides a list of all exposures identified.
The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
Full characteristics of the included studies are provided in Supplementary File 2.
After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.
These effects represent the findings of `r manuscript_info$effects_sum$sum_k` primary studies, involving `r manuscript_info$effects_sum$sum_n` participants.
The characteristics of the included effects are available in Supplementary File 3.

@@

## Education Outcomes

@@

## Health-related Outcomes

@@

There were a number of strengths and limitations to our work.
Our primary goal for this umbrella review was to provide a high-level synthesis of screen use research, by examining a range of exposures and the associations with a broad scope of outcomes.
Our results represent the findings from `r manuscript_info$effects_sum$sum_k` primary studies comprised of `r manuscript_info$effects_sum$sum_n` participants.
To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
